Estimating Gaze Duration Error from Eye Tracking Data

### 2022-07-24 paper/paper.tex
paper

In this work we develop an algorithm for estimating
the error bounds on gaze duration measurement through monte carlo simulation based on the content
of an eye tracking calibration log file. We provide this algorithm as an open source application
that allows for robust estimates of the error distribution of gaze duration measurements. 
We use this application to conduct experiments on the expected error bounds for different duration
measurements across a range of session lengths and area of interest positions within the viewport
of mobile devices. The results indicate that error in gaze duration estimation is sensitive to
the size of fixation error as well as the proportion of total field of view that the object occupies
and the proportion of viewing time that was taken with gaze fixation.

>>>>

In this work we develop an algorithm for estimating
the error distribution of gaze duration measurement through monte carlo simulation 
using the content of an eye tracking calibration log file. 
We provide this algorithm in an open source application
to allow researchers to understand the error in their gaze duration measurements. 
We use this application to conduct experiments on the expected error bounds for different duration
measurements across a fixed session length for a simulated advertising area of interest 
study on a mobile device. 
The results indicate that error in gaze duration estimation is sensitive to
fixation error beyond a bound that will depend on the size of interest and the session length.
